\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[margin=1in]{geometry}
\title{Curriculum Vitae}
\author{Brad Schoenrock}
\date{}
\begin{document}
\maketitle
\large
%\Large


\section{Education}
\hspace{0.5cm}PhD seeking Graduate Student MSU 2010-present

Masters Michigan State University 2012

REU at Cornell University 2009

B.S. physics and mathematics with minors in chemistry and computer science Northern Michigan University 2006-2010


\section{Research experience}
\hspace{0.5cm}Search for tZ final state in ATLAS, Advisor: Dr. Reinhard Schwienhorst

Calculation of Diboson cross sections at the LHC, Advisor: Dr. Reinhard Schwienhorst

Single top quark cross section measurement in the t-channel at the high-luminosity LHC, Snowmass 2013,  Advisor: Dr. Reinhard Schwienhorst

Creating the planetarium show "Relics of the Big Bang" for ATLAS outreach, Advisor: Dr. Reinhard Schwienhorst

Fitting reaction rates for astrophysically relevant nuclear processes, Advisor: Dr. Hendrik Schatz. 

Assembly of neutron detectors for a measurement of the electric form factor of the neutron, Advisor: Dr. William Tireman

Soil and sediment sampling project (Searching for Naturally Occurring Radioactive Materials) in Marquette MI, USA, Advisor: Dr. William Tireman


\section{Publications and Papers}
\hspace{0.5cm}Single top quark cross section measurement in the t-channel at the high-luminosity LHC
Brad Schoenrock, Elizabeth Drueke (Michigan State U.), Barbara Alvarez Gonzalez (Michigan State U. \& Cantabria Inst. of Phys.), Reinhard Schwienhorst (Michigan State U.). Aug 28, 2013. 16 pp.
e-Print: arXiv:1308.6307

Snowmass 2013 Top quark working group report
Top Quark Working Group Collaboration (K. Agashe (Convener) et al.). Nov 8, 2013. 54 pp.
e-Print: arXiv:1311.2028 

Searches for resonances in the tb and tc final states at the high-luminosity LHC
with contributions from the ATLAS Collaboration (Elizabeth Drueke et al.). Sep 26, 2013.
e-Print: arXiv:1309.7043


\section{Presentations}
\hspace{0.5cm}"Single top quark cross section measurement in the t-channel at the high-luminosity LHC" Snowmass proceedings, 2013

"Relics of the Big Bang-Live talks" Abrams planetarium, 2011

"Developing Automatic Test Electronics for Measuring the Performance of SRF Cavities" at Argonne National Laboratory’s Symposium for Undergraduates, 2009

"Neutron Detector Assembly for a High Precision Measurement of the Electric Form Factor of the Neutron" at Argonne National Laboratory’s Symposium for Undergraduates, 2008


\section{Languages}
\hspace{0.5cm}I am familiar with C++, root, LaTex, java, labview, MATLAB, some bash, some Visual Basic, and some assembly code. 


\section{Awards and Acknowledgements}
\hspace{0.5cm}AAPT Best Graduate TA, 2012-2013

Graduated Suma Cum Laude NMU, 2010

Honors Graduate, Northern Michigan University, 2010

Outstanding physics undergraduate Northern Michigan University, 2010


\section{Job experience}
\hspace{0.5cm}Research assistant MSU high energy physics group, 2010-present

Teaching Assistant, MSU physics department, Introductory Physics Laboratory 1, 2010

Research assistant National Superconducting Cyclotron Laboratory, 2010

Walk in tutor at NMU, Marquette MI, 2008-2010

Research assistant physics dept. at NMU, Marquette MI, 2008

Individual tutoring for Student Support Services (SSS) at NMU, 2007-2010

Walk in tutor for SSS, Marquette MI, 2007-2010

Study group tutor for SSS covering introductory physics 1 \& 2, Marquette MI, 2007-2010

Lab setups for the physics dept. at NMU, Marquette MI, 2007-2010



\end{document}

